Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2017-12-09 paper.tex
corrections

Beside scaling-down the ligand, also the atoms of the protein can be scaled, which is used e.g. in~\cite{cortes2005path}.
The tool~\cite{cortes2005path} uses the scale 0.8 for both the ligand and the protein.
We tested also this case using \RA\ (the column \RD\ in Tab.~\ref{tab::main}).
The results are same as for ligand scale $\smin=0.6$  (except DCP and m040 which can be a result of the randomization).

@@

Judging the accessibility of the active site by a ligand based only on the traversability rates may be problematic if the ligand is scaled down too much.
Instead of using a single version of the scaled-down ligand, we only limit the minimal scale used by the planner (the parameter $\smin$) and
the planner prefers to apply the higher scales if possible.
%The expansion step always prefers to expand the tree by a collision-free configuration with the maximal scale.
%that leads to a new collision-free configuration.
The information about the scales used at the trajectory points % (which can be extracted from the configuration tree of the proposed planner) 
brings the biochemists new knowledge about the tunnels, which was impossible to get using the VD-based computations.
The  visualization allows the biochemists to observe those parts of the tunnel where the ligand had to be scaled-down significantly (red parts of trajectories in Fig.~\ref{fig::dcp}), and parts where the ligand could be enlarged again (green parts in Fig.~\ref{fig::dcp}).
According to the results of the motion planing, the DCP needs to shrink down to ca. 75~\% of its size (Fig.~\ref{fig::dcp}, point B).
As both the protein and the ligand mutually influence each other, it is possible that even a narrow part of the tunnel is traversable.
This was observed in the MD simulation of the DCP ligand in the 4E46 protein, which revealed that DCP can pass the main tunnel~\cite{marques2017catalytic}.

>>>>

Beside scaling-down the ligand, also the atoms of the protein can be scaled, which is used e.g. in~\cite{cortes2005path}.
The tool~\cite{cortes2005path} uses the scale 0.8 for both the ligand and the protein.
We tested also this case using \RA\ (the column \RD\ in Tab.~\ref{tab::main}).
The results are close the results of \RA\ and $\smin=0.6$  (except DCP and m040 which can be a result of the randomization).

@@

Judging the accessibility of the active site by a ligand based only on the traversability rates may be problematic if the ligand is scaled down too much.
Instead of using a single version of the scaled-down ligand, we only limit the minimal scale used by the planner (the parameter $\smin$) and
the planner prefers to apply the higher scales if possible.
%The expansion step always prefers to expand the tree by a collision-free configuration with the maximal scale.
%that leads to a new collision-free configuration.
The information about the scales used at the trajectory points 
brings the biochemists new knowledge about the tunnels, which was impossible to get using the VD-based computations.
By visualizing all trajectories computed for different scales, we can observe those parts of the tunnel where the ligand had to be scaled-down significantly (red parts of trajectories in Fig.~\ref{fig::dcp}), and parts where the ligand could be enlarged again (green parts in Fig.~\ref{fig::dcp}).
According to the results of the motion planing, the DCP ligand needs to shrink down to ca. 75~\% of its size, but only at one part of the tunnel (Fig.~\ref{fig::dcp}, point B). 
Beyond this point, the ligand can move at larger scales again.
As both the protein and the ligand mutually influence each other, it is possible that even such a narrow part of the tunnel is traversable.
This was observed in a separate MD simulation of the DCP ligand in the 4E46 protein, which revealed that DCP can pass the main tunnel~\cite{marques2017catalytic}.
